Topological approach to finding blackholes in directed networks

### 2019-12-05 blackholes/pavt/article.tex
Section 1.1 is almost done

\section{Blackhole search in directed graph}
applications Anti-Money Laundering \cite{semenov2017survey}

\subsection{Task statement and Preliminaries}
In this section we provide some basic notations and definitions, which will be used in this paper.

Previously team of University of New Jersey gave \cite{li2010detecting} general and simplified problem formulation for blackhole search
in directed graph. In this paper we consider simplified problem formulation, applied to directed unweighted graph.

First, consider a directed graph G = G(V,E), where $V$ is the set of all nodes and E is the set if all edges.
Assume, that we deal with the general case of graph, without any special restrictions, unless the opposite is stated.

\begin{definition}{Blackhole}
Subset of nodes $B \in V$ is called a blackhole if there is no such pair of nodes $(u,v)$ that $u \in B$ and $v \in V \backslash B$
and $(u,v) \in E$. 
$G'(B, E')$ must form a weakly connected subgraph of G(V,E).
\end{definition}

The task is to find in unweighted directed graph as many blackholes as possible in restricted time.

@@

\begin{definition}
Given a directed graph $G(V,E),\ v_i \in V,\ e_i \in E$, where $e_i = (v_{i-1}, v_i)$. We say that sequence $v_0e_1v_1e_2v_2...e_{k}v_{k}$
forms a directed path from $v_0$ to $v_k$, if $v_i \neq v_j$ for all $0 <= i, j <= k, i \neq j$. The length of this directed path is $k$.
\end{definition}

\begin{definition}
Given a directed graph $G(V,E), u,v \in V$. We say that $v$ is reachable from $u$ if there is a directed path that starts from $u$ and ends at $v$.
\end{definition}

\begin{definition}
Given a directed graph $G(V,E), u,v \in V$. If $v$ is reachable from $u$, then we say $u$ is a predecessor of $v$ and $v$ is a successor if $u$.
If there is an edge from $u$ to $v$, then $u$ is a direct predecessor of $v$, and $v$ is a direct successor if $u$.
\end{definition}

\begin{definition}
Set of nodes in a directed graph is called a Strongly Connected Component(SCC) if every node is reachable from every other node.
\end{definition}

\begin{definition}
Given a directed graph $G(V,E), v \in V$. The closure of $v$, denoted as $Closure(v)$, is defined as $Closure(v) = \{u\ |\ there\ is\ a\ directed\ path\ from\ v\ to\ s\} \cup \{v\}$.
In other words: closure of node $v$ is a set of all nodes reachable from $v$, including $v$.
\end{definition}

The following lemmas will be given without proof. It is provided in \cite{li2010detecting}.

\begin{lemma}
If a node $v \in B$, where $B \subseteq V$ is a blackhole, then all the successors of $v$ are all in $B$.
\end{lemma}

\begin{lemma}
If a node $v \in B$, where $B \subseteq V$ is a blackhole, then closure of $v$ is a subset of $B$.
\end{lemma}

@@

\subsection{Related Work}
The main contributor to the topic is the New Jersey University. They both formulated the task and provided an algorithm for
blackhole detection in case of unweighted directed graph \cite{li2010detecting}. Two years later they published an algorithm
for approximate blackholes search in general case (weighted graph)\cite{li2012mining,li2014mining}. Hong et al \cite{hong2015detecting} had
an unusual application for blackhole mining in the city environment. They introduced original algorithm. Semenov et al. \cite{semenov2017survey}
in 2017 provided a survey of common approaches to anti - money laundering by graph mining.

@@

Another example is common SmallWorld\cite{watts1999networks} graph. It has most of its nodes in one large SCC, couple of leaves and couple of roots.
With iBlackhole algorithm and consequtive approach we will quickly discover all the small blackholes and then for a long time will try to discover
blackholes inside an SCC.

>>>>

\section{Blackhole Search in Directed Graph}
applications Anti-Money Laundering \cite{semenov2017survey}

\subsection{Problem Statement and Preliminaries}
In this section we provide some basic notations and definitions, which will be used in this paper. In this paper we consider simplified problem formulation, applied to directed unweighted graph.

First, consider a directed graph $G = G(V,E)$, where $V$ is a set of all nodes and $E$ is a set if all edges of the graph. 
\FIXME{Мне кажется, это лишнее предложение, так не пишут в статьях:} Assume that we deal with the general case of graph, without any special restrictions, unless the opposite is stated.

\begin{definition}
Subset of nodes $B \in V$ is called a blackhole if  the following two conditions are satisfied: 
1) Subgraph $G'(B, E')$ induced by $B$ is weakly connected, 
%$|B| \geq 2$,
and
2) there is no such pair of nodes $(u,v)$ that $u \in B$, $v \in V \backslash B$ and $(u,v) \in E$.
\end{definition}

The goal is to find in unweighted directed graph as many blackholes as possible in restricted time.

@@

\FIXME{Удалил возможные кратные ребра в определении 2, это важно?}
\begin{definition}
For a given directed graph $G(V,E)$ we say that sequence $v_0v_1v_2...v_{k}$ of $v_i \in V, 0 \leq i \leq k$ forms a directed path from $v_0$ to $v_k$, if there are edges $(v_{i-1}, v_i) \in E, 1 \leq i \leq k$ and $v_i \neq v_j$ for all $0 \leq i, j \leq k, i \neq j$. The length of this directed path is $k$.
\end{definition}

\begin{definition}
For a given directed graph $G(V,E)$ we say that $v \in V$ is reachable from $u \in V$ if there is a directed path that starts from $u$ and ends at $v$.
\end{definition}

\begin{definition}
For a given directed graph $G(V,E)$ if $v \in V$ is reachable from $u \in V$, then we say $u$ is a predecessor of $v$ and $v$ is a successor if $u$.
If there is an edge from $u$ to $v$, then $u$ is a direct predecessor of $v$, and $v$ is a direct successor if $u$.
\end{definition}

\begin{definition}
Set of nodes in a directed graph $G$ is called a Strongly Connected Component (SCC) if every node of $G$ is reachable from every other node of $G$.
\end{definition}

\begin{definition}
For a given directed graph $G(V,E)$. The closure of $v \in V$ is $Closure(v) = \{u\ |\ there\ is\ a\ directed\ path\ from\ v\ to\ u\} \cup \{v\}$.
In other words, a closure of node $v$ is a set of all nodes reachable from $v$, including $v$.
\end{definition}

The following lemmas are proved in \cite{li2010detecting}.

\begin{lemma}
If a node $v \in B$, where $B \subseteq V$ is a blackhole, then all the successors of $v$ are in $B$.
\end{lemma}

\begin{lemma}
If a node $v \in B$, where $B \subseteq V$ is a blackhole, then the closure of $v$ is a subset of $B$.
\end{lemma}

@@

\subsection{Related Work}

% Previously 
Authors from the University of New Jersey gave \cite{li2010detecting} general and simplified problem formulation for blackhole search
in directed graph.

The main contributor to the topic is the New Jersey University. They both formulated the task and provided an algorithm for
blackhole detection in case of unweighted directed graph \cite{li2010detecting}. Two years later they published an algorithm
for approximate blackholes search in general case (weighted graph)\cite{li2012mining,li2014mining}. Hong et al \cite{hong2015detecting} had
an unusual application for blackhole mining in the city environment. They introduced original algorithm. Semenov et al. \cite{semenov2017survey}
in 2017 provided a survey of common approaches to anti - money laundering by graph mining.

@@

Another example is common SmallWorld \cite{watts1999networks} graph. It has most of its nodes in one large SCC, couple of leaves and couple of roots.
With iBlackhole algorithm and consequtive approach we will quickly discover all the small blackholes and then for a long time will try to discover
blackholes inside an SCC.
